### 2021-09-08 README.Rmd
add cleaned up education state data

```{r}
library(conmat)
# build synthetic age-structured contact matrices with GAMs
# analysis of polymod data

@@

```{r}
# predict contacts at 1y and 5y resolutions for inspection
synthetic_all_5y <- predict_contacts(
  model = m_all, 
  population = get_polymod_population(),
  age_breaks = age_breaks_5y
) %>%
  predictions_to_matrix()

@@

```{r matrix-plot}
# predict contacts at 1y and 5y resolutions for inspection
synthetic_all_5y <- predict_contacts(
  model = m_all, 
  population = get_polymod_population(),
  age_breaks = age_breaks_5y
) %>%
  predictions_to_matrix()

@@

>>>>

```{r example}
library(conmat)
# build synthetic age-structured contact matrices with GAMs
# analysis of polymod data

@@

```{r syn-all-5y}
# predict contacts at 1y and 5y resolutions for inspection
synthetic_all_5y <- predict_contacts(
  model = m_all, 
  population = get_polymod_population(),
  age_breaks = age_breaks_5y
) %>%
  predictions_to_matrix()

@@

```{r matrix-plot}
set.seed(2021-09-08)
# predict contacts at 1y and 5y resolutions for inspection
synthetic_all_5y <- predict_contacts(
  model = m_all, 
  population = get_polymod_population(),
  age_breaks = age_breaks_5y
) %>%
  predictions_to_matrix()

@@

## Data sources

This package provides data for use in calculating contact matrices.

These data are still being cleaned and processed, but their current forms are shown below:

### abs_education_state

```{r abs-education-state}
abs_education_state
```

### abs_education_state_2020

```{r abs-education-state-2020}
abs_education_state_2020
```

### abs_employ_age_lga

```{r abs-employ-age-lga}
abs_employ_age_lga
```

### abs_household_lga

```{r abs-household-lga}
abs_household_lga
```

### abs_pop_age_lga_2016

```{r abs-pop-age-lga-2016}
abs_pop_age_lga_2016
```

### abs_pop_age_lga_2020

```{r abs-pop-age-lga-2020}
abs_pop_age_lga_2020
```

### abs_state_age

```{r abs-state-age}
abs_state_age
```
